A Bioconductor workflow for processing and analysing spatial proteomics data

### 2018-05-22 replies-to-reviewers.Rmd

The results are already available as a `RDS` file and stored in
`pRolocdata` for users. This is what is called in the manuscript under
the hood:

```
f0 <- dir(extdatadir, full.names = TRUE, pattern = "bpw-pdres.rds")
pdres <- readRDS(f0)
hl <- addMarkers(hl, pdres, mcol = "pd", verbose = FALSE)
```

We have made this code available in the manuscript in an appendix so
users can continue to produce the exact plots as they see in this
workflow.

> The above comment is of course also true for the KNN TL Optimisation
> on page 33 - this needs to be downloadable, since not everyone has
> access to Cambridge's HPC and probably even less have 76 hours to
> spare.

@@

We have now referenced Figure 16 in the text and made sure that the
code chunks and figures follow inline where they are referenced in the
text.

> On page 28: ...by extracting the median or 3rd quantile score per
> organelle? do you mean quartile? Otherwise I do not follow.

Thank you, yes this is a typo and has now been changed to 'quartile'.

> On page 32: package to query the relevent database *relevant*

@@

This typo has been rectified.

> On page 32 - there is something wrong with this sentence: To remove
> the 4 classes and create a new column of markers in the feature data
> called tlmarkers to use for the analysis:

This sentence is not needed here and so it has now been removed as it
essentially reiterates what is said in the above paragraph.

> On page 34: From examining the parameter seach plots as described in
> section Optimisation... search!

@@

This typo has been rectified.

> On page 36: and later reload the object using save. -> that would be
> `load` then!

@@

Many thanks for your comments, we have responded to them inset below.

### A few comments:

> Some clearer statement early on would help to clarify for readers
> what types of data this works with. I know that the authors indicate
> that the example they use is 10-plex TMT and that it can be used
> with label-free or other labels, but that is not what I am referring
> to. Rather, structure of the experiment. That is, that one needs
> systematic quantitative data on all the different relevant fractions
> from a cell, as opposed to someone who perhaps did a differential
> centrifugation experiment to isolate a couple fractions and then
> wants to apply this (my understanding is that this latter example
> would not be usable).

From a purely technical point of view, we need a data matrix with
features (typically proteins or protein groups) along the rows and
sub-cellular fractions along the columns. Given the requirement for
complete (or near-complete) quantitative vectors along all fractions
to assure best results, a data set that would only contain one
quantitation value per fraction would not work. However, separation
using differential centrifugation, or any separation that generates
rganelle-specific separation profiles is a good fit for pRoloc. For
instance, the type of data generated by methods such as described in
Itzhak et al. (2016)[^1] are well fitted for our software:

```{r plot2d, message = FALSE, fig.width = 6, fig.height = 6}
library(pRoloc)
library(pRolocdata)
data(itzhak2016stcSILAC)
## 6 combined replicates of 5 fractions each
dim(itzhak2016stcSILAC)
plot2D(itzhak2016stcSILAC)
addLegend(itzhak2016stcSILAC, where = "topright", cex = .7)
```

[^1]: Itzhak DN, Tyanova S, Cox J, Borner GH. Global, quantitative and dynamic mapping of protein subcellular localization. Elife. 2016 Jun 9;5. pii: e16950.  doi: 10.7554/eLife.16950. PubMed PMID: 27278775; PubMed Central PMCID: PMC4959882.

### 2018-05-23 replies-to-reviewers.Rmd

Many thanks for your comments, we have responded to them inset below.

### A few comments:

> Some clearer statement early on would help to clarify for readers
> what types of data this works with. I know that the authors indicate
> that the example they use is 10-plex TMT and that it can be used
> with label-free or other labels, but that is not what I am referring
> to. Rather, structure of the experiment. That is, that one needs
> systematic quantitative data on all the different relevant fractions
> from a cell, as opposed to someone who perhaps did a differential
> centrifugation experiment to isolate a couple fractions and then
> wants to apply this (my understanding is that this latter example
> would not be usable).

From a purely technical point of view, we need a data matrix with
features (typically proteins or protein groups) along the rows and
sub-cellular fractions along the columns. Given the requirement for
complete (or near-complete) quantitative vectors along all fractions
to assure best results, a data set that would only contain one
quantitation value per fraction would not work. However, separation
using differential centrifugation, or any separation that generates
organelle-specific separation profiles is a good fit for pRoloc. For
instance, the type of data generated by methods such as described in
Itzhak et al. (2016)[^1] are well fitted for our software:
